Specialisation \& the Latitude-niche-breadth Hypothesis

### 2015-10-11 talk/ABC_2015.tex
?

>>>>

  \begin{frame}{Estuarine, Marine, \& Terrestrial Food Webs}
    \begin{center}
      \includegraphics*[width=.8\textwidth]{Figures/results/no_effect.eps}

      \vspace{1cm}
      {\color{white} No effect of latitude on scaling\\
      Similar niche widths at all latitude\\
      Supports Davies \emph{et. al.}, 2007:\\
      Broader niche space in the tropics}

  \begin{frame}{Estuarine, Marine, \& Terrestrial Food Webs}
    \begin{center}
      \includegraphics*[width=.8\textwidth]{Figures/results/no_effect.eps}

      \vspace{1cm}
      No effect of latitude on scaling\\
      {\color{white}Similar niche widths at all latitude\\
      Supports Davies \emph{et. al.}, 2007:\\
      Broader niche space in the tropics}

  \begin{frame}{Estuarine, Marine, \& Terrestrial Food Webs}
    \begin{center}
      \includegraphics*[width=.8\textwidth]{Figures/results/no_effect.eps}

      \vspace{1cm}
      No effect of latitude on scaling\\
      Similar niche widths at all latitude\\
      {\color{white} Supports Davies \emph{et. al.}, 2007:\\
      Broader niche space in the tropics}

  \begin{frame}{Estuarine, Marine, \& Terrestrial Food Webs}
    \begin{center}
      \includegraphics*[width=.8\textwidth]{Figures/results/no_effect.eps}

      \vspace{1cm}
      No effect of latitude on scaling\\
      Similar niche widths at all latitude\\
      Supports Davies \emph{et. al.}, 2007:\\
      Broader niche space in the tropics

  \begin{frame}{Lake \& Stream Food Webs}
    \begin{center}
      \includegraphics*[width=.8\textwidth]{Figures/results/effect.eps}

      \vspace{1cm}
      {\color{white} Scaling increases with latitude\\
      Narrower niches in the tropics\\
      Supports Vazquez \& Stevens 2004\\}
      {\color{white} narrower niches in the tropics}

  \begin{frame}{Lake \& Stream Food Webs}
    \begin{center}
      \includegraphics*[width=.8\textwidth]{Figures/results/effect.eps}

      \vspace{1cm}
      Scaling increases with latitude\\
      {\color{white} Narrower niches in the tropics\\
      Supports Vazquez \& Stevens 2004\\}
      {\color{white} narrower niches in the tropics}

  \begin{frame}{Lake \& Stream Food Webs}
    \begin{center}
      \includegraphics*[width=.8\textwidth]{Figures/results/effect.eps}

      \vspace{1cm}
      Scaling increases with latitude\\
      Narrower niches in the tropics\\
      {\color{white} Supports Vazquez \& Stevens 2004\\}
      {\color{white} narrower niches in the tropics}

  \begin{frame}{Lake \& Stream Food Webs}
    \begin{center}
      \includegraphics*[width=.8\textwidth]{Figures/results/effect.eps}

      \vspace{1cm}
      Scaling increases with latitude\\
      Narrower niches in the tropics\\
      Supports Vazquez \& Stevens 2004\\
      {\color{white} narrower niches in the tropics}

  \begin{frame}{What's different in freshwaters?}
    Seasonality?\\
    NZ streams are weird but probably don't affect much\\
    Gape limitation?\\
  \end{frame}
